Tree-structured neural networks revisited

### 2016-03-03 writing/hard_stack_paper/paper.tex
Filling out more of the paper.

\makeatletter
\newcommand{\@BIBLABEL}{\@emptybiblabel}
\newcommand{\@emptybiblabel}[1]{}
\definecolor{black}{rgb}{0,0,0}
\makeatother
\usepackage[breaklinks, colorlinks, linkcolor=black, urlcolor=black, citecolor=black, draft]{hyperref}

@@

\begin{document}
\maketitle
\begin{abstract}
\begin{itemize}
\item TreeRNNs are great, don't work for big data.
\item We present the transition-based TreeRNN implementation -- makes efficient training possible, show that it helps relative to seq models.
\item Further, attention has proven powerful for extending sequence models. We introduce constit-by-constit attention, and find it to be effective here, too.
\end{itemize}
\end{abstract}

@@

\item Attention issues
\begin{itemize}
\item The technique of soft attention has proven to be exceptionally effective as a way of training neural network models for tasks like translation \cite{bahdanau2014neural,luong-pham-manning:2015:EMNLP} and natural language inference \cite{rocktaschel2015reasoning}.
\item This paper proposes two complementary extensions of the idea of attention to tree-structured models:
\begin{itemize}
\item Constituent-by-constituent attention, in which each node in the tree of one sentence is given a soft alignment to some node or nodes in a second sentence.
\item The mTreeLSTM, which uses a third tree structured model to accumulate information about the alignment between two sentences into a single feature vector. This builds on the notion of a matching LSTM or mLSTM from \citealt{DBLP:journals/corr/WangJ15b}.
\end{itemize}
\end{itemize}
\end{itemize}

@@

@@

@@

\paragraph{The classifier}

@@

\paragraph{The Stanford Natural Language Inference task} 
We evaluate our model on the Stanford Natural Language Inference task \cite{snli:emnlp2015}.

550k/10k/10k split

We skip unlabeled examples.

\todo{[SB] Pull out an example from SNLI.}

@@

                        & 1.4m               &   92.3   &   89.1      \\
\midrule
\multicolumn{4}{c}{New results}\\
\midrule150d LSTM RNN           & ?                  &   ?      &   81?       \\
150d TB TreeLSTM    
                        & ?                  &   ?      &   82?       \\
150d TB TreeLSTM w/ tracking    
                        & ?                  &   ?      &   82?       \\
150d TB TreeLSTM w/ tracking, sequence-based attn.        
                        & ?                  &   ?      &   82?       \\
150d TB TreeLSTM w/ tracking, tree-based attn.            
                        & ?                  &   ?      &   \textbf{82?}\\
    \bottomrule
  \end{tabular}
  \protect\caption{\protect\label{tab:results}Results on SNLI 3-way inference classification. All reported figures are percent accuracy. \todo{Add seconds-per-step *if* we get a reasonably well-optimized model in time.}} 
\end{table*}

@@

Evaluation metrics: Time per minibatch on a jag machine, with and without GPU access.

@@

\begin{itemize}
\item It is possible to train a tree-structured model, without approximation, on large-scale language learning tasks.
\item Tree structure helps in large-scale language learning tasks. Not massively, but measurably.
\item The advantages of attention carry over to tree-structured models.
\item Future work: Encode the stack, after \citealt{dyer-EtAl:2015:ACL-IJCNLP}
\item Future work: Incorporate the parser
\item Future work: Latent parses
\end{itemize}

@@

(some of) the Tesla K40(s) used for this research was/were donated by the NVIDIA Corporation.

\bibliographystyle{../acl}
\bibliography{../MLSemantics}

>>>>

\makeatletter
\newcommand{\@BIBLABEL}{\@emptybiblabel}
\newcommand{\@emptybiblabel}[1]{}
\definecolor{black}{rgb}{0,0,0}
\makeatother
\usepackage[breaklinks, colorlinks, linkcolor=black, urlcolor=black, citecolor=black]{hyperref}

@@

\begin{document}
\maketitle
\begin{abstract}
\begin{itemize}
\item TreeRNNs are great, don't work for big data.
\item We present the transition-based TreeRNN implementation -- makes efficient training possible, show that it helps relative to seq models.
\item Further, attention has proven powerful for extending sequence models. We introduce constituent-by-constituent attention, and find it to be effective here, too.
\end{itemize}
\end{abstract}

@@

\item Attention issues
\begin{itemize}
\item The technique of soft attention has proven to be exceptionally effective as a way of training neural network models for tasks like translation \cite{bahdanau2014neural,luong-pham-manning:2015:EMNLP} and natural language inference \cite{rocktaschel2015reasoning}.
\item This paper proposes two complementary extensions of the idea of attention to tree-structured models:
\begin{itemize}
\item Constituent-by-constituent attention, in which each node in the tree of one sentence is given a soft alignment to some node or nodes in a second sentence.
\item The mTreeLSTM, which uses a third tree structured model to accumulate information about the alignment between two sentences into a single feature vector. This builds on the notion of a matching LSTM or mLSTM from \citealt{DBLP:journals/corr/WangJ15b}.
\end{itemize}
\end{itemize}

\item Outline of the paper
\begin{itemize}
\item Propose a model
\item Show how the model can be used for NLI
\item Show how attention can be used on the NLI model
\item Experiments and discussion
\end{itemize}

@@

\todo{[SB] Finish this subsection.}

@@

When a \reduce~operation is performed, vector representations of two tree nodes are popped off of the head of the stack and fed into a {\ii composition function}, which is a neural network function that produces

@@

\paragraph{Creating a sentence pair classifier}

@@

\subsection{Natural language inference and SNLI}

We evaluate our model on the task of natural language inference (NLI), also known as recognizing textual entailment (RTE). NLI is a sentence pair classification task, in which a model reads two sentences (a premise and a hypothesis), and outputs a judgment of {\it entailment}, {\it contradiction}, or {\it neutral}, reflecting the relationship between the meanings of the two sentences, as here:

\begin{quote}
Premise: {\it Girl in a red coat, blue head wrap and jeans is making a snow angel.}

Hypothesis: {\it A girl outside plays in the snow.}

Correct label: {\it entailment}
\end{quote}

Even though NLI is framed as a relatively simple three-way classification task, it is nonetheless an effective way of evaluating the ability of some model to extract broadly informative representations of sentence meaning. In order for a model to reliably perform well on NLI across a range of sentence types and text genres, it must be able to represent and reason with all of the core phenomena of natural language semantics, including quantification, coreference, scope, and several types of ambiguity.

In particular, we use the Stanford NLI corpus (SNLI, \citealt{snli:emnlp2015}). SNLI is a corpus of 570k human-labeled pairs of scene descriptions like the one above. We use the standard train--test split and ignore unlabeled examples, which leaves about 549k examples for training, 9,842 for development, and 9,824 for testing. SNLI labels are roughly balanced, with the most frequent label, {\it entailment}, making up 34.2\% of the test set.

\subsection{Models evaluated}

@@

                        & 1.4m               &   92.3   &   89.1      \\
\midrule
\multicolumn{4}{c}{New results}\\
\midrule
\result{150d LSTM RNN      }     & ?                  &   ?      &   ?       \\
\result{150d TB TreeLSTM}   
                        & ?                  &   ?      &   ?       \\
\result{150d TB TreeLSTM w/ tracking    }
                        & ?                  &   ?      &   ?       \\
\result{150d TB TreeLSTM w/ tracking, sequence-based attn.   }     
                        & ?                  &   ?      &   ?       \\
\result{150d TB TreeLSTM w/ tracking, tree-based attn. }           
                        & ?                  &   ?      &   \textbf{?}\\
    \bottomrule
  \end{tabular}
  \protect\caption{\protect\label{tab:results}Results on SNLI 3-way inference classification. All reported figures are percent accuracy. \result{[JG]Add seconds-per-step *if* we get a reasonably well-optimized model in time.}} 
\end{table*}

@@

@@

\begin{itemize}
\item It is possible to train a tree-structured model, without approximation, on large-scale language learning tasks.
\item Tree structure helps in large-scale language learning tasks. Not massively, but measurably.
\item The advantages of attention carry over to tree-structured models.
\end{itemize}

\paragraph{Future work} The tracking LSTM that we incorporated into our model uses only simple, quick to compute features drawn from the head of the buffer and the head of the stack. It is plausible that giving the tracking LSTM access to more information from the buffer and stack at each step would allow it to better represent the context of each tree node, including information about that nodes neighbors in the sentence string and its likely position in the final tree, and that that context information could support better sentence encoding. One promising way to pursue this goal would be to encode the full contents of the stack and buffer at each time step following the method used by \citealt{dyer-EtAl:2015:ACL-IJCNLP} for parsing.
The model presented here is only capable of operating over sentences which have already been assigned a binary constituency tree by a parser. This is not necessarily a practical limitation, since modern parsers can assign reasonably high quality parses in so little time as to not dramatically impact the performance characteristics of our model \todo{[SB,JG,CM] How fast are fast constit parsers?}. However, depending upon an external parser can be a missed opportunity.

In future work, we aim to incorporate a parser into our model, allowing it to simultaneously learn to parse sentences (using a conventional parsing objective function) and to use those parses to learn semantic representations for those sentences (using a classification objective function, as in this work). Implementing such a model on top of our proposed stack-based design would learn a model that could productively share representations between the two tasks. Implementing such a model on top of a differentiable version of our stack-based design (possibly following \citealt{grefenstette2015learning} \todo{[SB] Cite FAIR stack paper.}) would further make it possible for the model to learn to parse using guidance from the semantic representation objective, essentially allowing  learn to produce parses that are, in aggregate, better suited to supporting semantic interpretation than those supplied in the training data.

@@

Some of the Tesla K40(s) used for this research was/were donated by the NVIDIA Corporation.
\todo{[CM,CP] Acknowledge other grants.}

\bibliographystyle{../acl}
\bibliography{../MLSemantics}
\todo{[SB] Make bibliography style uniform.}
